---
title: "ctmm objects and information"
output: html_document
date: "2024-07-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ctmm

When convert into as.telemetry() object, ctmm will create a dataframe with the following columns, they also may be in a list if there is  tracking data for multiple individuals

```{r}
names(test)
# [1] "timestamp" "longitude" "latitude"  "t"         "HDOP"      "x"         "y" 
```

description of each column:

timestamp: The original time data, usually in a date-time format.
longitude: The longitude coordinate of the tracking data.
latitude: The latitude coordinate of the tracking data.
t: Numeric representation of the timestamp, often used for calculations.
HDOP: Horizontal Dilution of Precision, a measure of the accuracy of the GPS data.
x: The x-coordinate in a projected coordinate system (e.g., UTM).
y: The y-coordinate in a projected coordinate system (e.g., UTM).

Example:

head(test)
               timestamp longitude latitude          t HDOP          x        y
2374 2023-01-01 02:45:38 -120.1634 49.03759 1672569938  1.4  -899.0965 1028.434
2375 2023-01-01 09:01:56 -120.1635 49.03758 1672592516  1.4  -905.3372 1021.851
2376 2023-01-01 15:15:38 -120.1623 49.04228 1672614938  1.8 -1136.9943 1499.506
2377 2023-01-01 21:30:37 -120.1626 49.03711 1672637437  1.8  -823.0678 1016.954
2378 2023-01-02 03:45:38 -120.1629 49.03842 1672659938  1.4  -925.5369 1123.293
2379 2023-01-02 10:00:38 -120.1634 49.03747 1672682438  2.0  -892.6918 1015.719

'1672569938'  means 2023-01-01 02:45:38

t = contains the Unix timestamp, which is the number of seconds that have elapsed since 00:00:00 UTC on 1 January 1970 (also known as the Unix epoch)

To convert Unix timestamp to regular format use:
```{r}
timestamp_example <- 1672569938
converted_time <- as.POSIXct(timestamp_example, origin="1970-01-01", tz="UTC")
converted_time
# [1] "2023-01-01 02:45:38 UTC"
```

